EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-11 draft.tex
Update draft.tex
Update developer  point of view

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
\section{Container-based application} 
\label{docker}

@@

% Do we need a description of every container? Wouldn't a general 
% description  of the containers used be enough? - JJ 
% Ok, I thin only workers and the controller need to be described in detail - Mario 
\subsection{Message Queue Container} 
\label{message_container}

@@

In the case of the first level of integration, developers
can implement a new stateless Docker container following
the description in the previous section (\ref{workers}). The worker
container executes a daemon that continuously pulls messages from the input queue
on the Redis host specified as an environment variable {\texttt REDIS\_HOST}. If the new
population-based algorithm is written in Python, developers can base the new
implementation on the provided worker container image, adding a new algorithm
function and worker and modifying the \texttt{main.py} file. 
The worker must include a constructor with the configuration dictionary 
(see Listing \ref{code:config}) as the only parameter, and call a the new function 
with the required parameters, unpacking them from the configuration dictionary if necessary.
All the code of the EvoSwarm Application is published with the open source MIT license.
% say which function, what's its API, how can you test it - JJ
% this is not an API the need to write their own - Mario
% We can write an API later - M
% Anyway you need to say what is the signature of the function. 
% Also, if they can use the existing implementation, you need to specify the license - JJ u
% Any reaction to this? - JJ

@@

For the secondary level of integration, developers need to add code to the setup
container %maybe you should specify more, at the beginning of the section, what is the current setup, what containers are there, what libraries are being used, and so no. - JJ 
to specify additional configuration options. For instance,  % related to? What do you mean here?
in the current configuration message (see Listing \ref{code:config})
workers executing a GA, initialize the mutation and crossover 
probabilities randomly from a specific range of values. Users specify
this range on the experiment configuration. 
Migration between populations is independent of the type of algorithm, as the
controller treats messages as the same type of objects. But developers could
also change the controller to specify new rules of operation, for instance, to
change the type of migration depending on the algorithm. 
For example, in the case of swarm-based algorithms,  migration between  
populations (swarms) can follow a topology, indicating valid connections 
between them (i.e., ring or hypercube). The controller
can apply these rules selectively only to swarm-based algorithms. In general, these configuration options will be algorithm and library specific.

On either level of integration, algorithm developers can upload the container
definition or images directly to a public repository like DockerHub. % Clarify what you need to change in those images. Will you need to just rebuild the image with new code, or something else? - JJ
Another
option is to upload the container image definition (Dockerfile) to GitHub and
define a trigger to re-upload the image to the registry after an update. Having
images publicly available can contribute to the reproducibility of experiments.
Moreover, having more algorithms available can benefit researchers trying to
compare against other algorithms or increase the diversity of their algorithms
by adding more search methods. Finally, in some cloud services, having hosted 
images is a requirement, as it is the case of Amazon ECS.

% Besides addressing the concerns of a reviewer, you should mention how this is related to the overall objective of the paper, saying this contributes to reproducibility or to be able to do it on the cloud  - Jj

@@

% This is only an idea of the section
%
% First you have to say that cloud is a way of describing deployment to any kind of infrastructure in a reproducible way, and it needn't be in the cloud proper, it can be deployed to anything, that's precisely the thing. But make clear that when you use a cloud provider, there are more options to do it... - JJ
% You should start writing this out soon... Don't leave it this way - JJ
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ

>>>>

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
% done - Mario 
\section{Container-based application} 
\label{docker}

@@

% Do we need a description of every container? Wouldn't a general 
% description  of the containers used be enough? - JJ 
% Ok, I think only workers and the controller need to be described in detail - Mario 
\subsection{Message Queue Container} 
\label{message_container}

@@

In the case of the first level of integration, developers
can implement a new stateless Docker container following
the description in the previous section (\ref{workers}). The worker
container executes a daemon that continuously pulls messages from the input queue
on the Redis host specified as an environment variable {\texttt REDIS\_HOST}. If the new
population-based algorithm is written in Python, developers can base the new
implementation on the provided worker container image, adding a new algorithm
function and worker and modifying the \texttt{main.py} file. 
The worker must include a constructor with the configuration dictionary 
(see Listing \ref{code:config}) as the only parameter, and call a the new function 
with the required parameters, unpacking them from the configuration dictionary if necessary.
All the code of the EvoSwarm Application is published with the open source MIT license.
% say which function, what's its API, how can you test it - JJ
% this is not an API the need to write their own - Mario
% We can write an API later - M
% Anyway you need to say what is the signature of the function. 
% Also, if they can use the existing implementation, you need to specify the license - JJ u
% Any reaction to this? - JJ
% I forgot to put done, but I added in the above paragraphs. It was correct? - Mario

@@

For the secondary level of integration, developers need to add code to the setup

container %maybe you should specify more, at the beginning of the section, 
% what is the current setup, what containers are there, what libraries are being used, and so on. - JJ
% The previous section talks about, can you have look? Maybe I should move it to this one. - Mario
% If not, I will add a remainder, something like: following from the setup described in the previous section... - M  
to specify additional configuration options. For instance,  % related to? What do you mean here? - done Mario 
in the current configuration message (see Listing \ref{code:config})
workers executing a GA, initialize the mutation and crossover 
probabilities randomly from a specific range of values. Users specify
this range on the experiment configuration. 
Migration between populations is independent of the type of algorithm, as the
controller treats messages as the same type of objects. But developers could
also change the controller to specify new rules of operation, for instance, to
change the type of migration depending on the algorithm. 
For example, in the case of swarm-based algorithms,  migration between  
populations (swarms) can follow a topology, indicating valid connections 
between them (i.e., ring or hypercube). The controller
can apply these rules selectively only to swarm-based algorithms. 
In general, these configuration options will be algorithm and library specific.

On either level of integration and after making the changes outlined before,
algorithm developers can upload the container 
definition or images directly to a public repository like DockerHub. 
% Clarify what you need to change in those images. 
% Added a brief comment at the beginning  - M
% Will you need to 
% just rebuild the image with new code, or something else? - JJ
% That and document your work, talk about this at the end - M
% We need to document our own images :) - M

Another option is to upload the container image definition (Dockerfile) to GitHub and
define a trigger to re-upload the image to the registry after an update. Having
images publicly available can contribute to the reproducibility of experiments.
Moreover, having more algorithms available can benefit researchers trying to
compare against other algorithms or increase the diversity of their algorithms
by adding more search methods. Finally, in some cloud services, having hosted 
images is a requirement, as it is the case of Amazon ECS.

% Besides addressing the concerns of a reviewer, you should mention how this is 
% related to the overall objective of the paper, saying this contributes to
% reproducibility or to be able to do it on the cloud  - Jj
% Added the lines bellow - Mario

Moreover, public repositories have the functionality for documenting, sharing,
and tracking different versions of both images and image definitions by using
tags. This infrastructure supports the objective of the paper, which is to
contribute to the reproducibility of experiments and platform independence.

@@

% This is only an idea of the section
%

% First you have to say that cloud is a way of describing deployment to any kind
% of infrastructure in a reproducible way, and it needn't be in the cloud proper,
% it can be deployed to anything, that's precisely the thing. But make clear that
% when you use a cloud provider, there are more options to do it... - JJ

% You should start writing this out soon... Don't leave it this way - JJ
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ
